---
title: "New-gctb_0.01maf"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{bash}
##################
##################
#With new subset of SNPs generated by initial filtering with a maf of 0.01 and genotyping rate of 90% (#14043083 SNPs), which were then used for LD pruning with --indep-pairwise 50 5 0.1 option to further reduce number of SNPs to #1784258 SNPs. This ~1.8 mi SNPs was used to obtain top 10 PCs for downstream analysis.
##################
##################
#no PCs-run1
###############

#!/bin/sh

#SBATCH --array=1-37

#SBATCH --job-name=37pheno_gctb_nopcs

#SBATCH --time=4:00:00

#SBATCH --mem-per-cpu=20G

#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_allchr_%J.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_allchr_%J.out

cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/

module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0


#without covariates

#mpirun -np 1 gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf0005_geno1_maf001subset --pheno  pheno_282_n37_new.txt --mpheno 9 --bayes S --S 0.11  --pi 0.1 --hsq 0.73 --chain-length 41000 --burn-in 1000 --out KRN_gctb_run2_nopcs > KRN_gctb_run2_nopcs.log 2>&1
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --mpheno ${SLURM_ARRAY_TASK_ID} --bayes S --pi 0.1 --hsq 0.5 --chain-length 1100 --burn-in 100 --out Trait${SLURM_ARRAY_TASK_ID}_gctb_run1_nopcs > Trait${SLURM_ARRAY_TASK_ID}_gctb_run1_nopcs.log 2>&1



##################
#Ten PCs-run1
###############
#!/bin/sh

#SBATCH --array=1-37

#SBATCH --job-name=37pheno_gctb_10pcs

#SBATCH --time=4:00:00

#SBATCH --mem-per-cpu=20G

#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_allchr_%J.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_allchr_%J.out

cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/

module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0


#without covariates

#mpirun -np 1 gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf0005_geno1_maf001subset --pheno  pheno_282_n37_new.txt --mpheno 9 --bayes S --S 0.11  --pi 0.1 --hsq 0.73 --chain-length 41000 --burn-in 1000 --out KRN_gctb_run2_nopcs > KRN_gctb_run2_nopcs.log 2>&1
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno ${SLURM_ARRAY_TASK_ID} --bayes S --pi 0.1 --hsq 0.5 --chain-length 1100 --burn-in 100 --out Trait${SLURM_ARRAY_TASK_ID}_gctb_run1_nopcs > Trait${SLURM_ARRAY_TASK_ID}_gctb_run1_nopcs.log 2>&1                                                                                                                                                               

```

```

```{r}
##grab results from run1
get_gctb_parres <- function(path="/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/Traits_parres"){
  # df: must contain "FID" (family id), "IID" (individual id)
  # cols: the idx of the phenotype columns
  
  files <- list.files(path, pattern="parRes", full.names = TRUE)
  message(sprintf("###>>> [%s] files detected!", length(files)))
  
  res <- data.frame()
  for(i in 1:length(files)){
    ### read in the file by skip the first two rows:
    pres <- read.table(files[i], skip = 2)
    pres$par <- row.names(pres)
    pres$file <- files[i]
    pres$trait <- gsub(".*/|.parRes", "", pres$file)
    res <- rbind(res, pres)
  }
  return(res)
}

### 
out <- get_gctb_parres(path="/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/Traits_parres")
s <- subset(out, par == "S")

pi <- subset(out, par == "Pi")

hsq <- subset(out, par == "hsq")

sel=s[,c(1,2,5)]
pi_ss=pi[,c(1,2,5)]
hsq_ss=hsq[,c(1,2,5)]

mdata=cbind(sel,pi_ss,hsq_ss)

mdata=subset(mdata,select=c(3,4,1,8,5,12,9))


```

```{bash}

########################
#Posterior values from run 1 was extracted using the above R script into an excel sheet to further process the script for run2.
##################
#No PCs-run2
###############
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T1
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T1.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T1.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno 1 --bayes S --S 0.01282 --pi 0.100037 --hsq 0.852065 --chain-length 41000 --burn-in 1000 --out Trait1_gctb_run2_nopcs > Trait1_gctb_run2_nopcs.log 2>&1
																							
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T2
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T2.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T2.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --mpheno  2 --bayes S --S -0.041524 --pi 0.106765 --hsq 0.75753 --chain-length 41000 --burn-in 1000 --out Trait2_gctb_run2_nopcs > Trait2_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T3
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T3.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T3.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  3 --bayes S --S 0.002019 --pi 0.092545 --hsq 0.94322 --chain-length 41000 --burn-in 1000 --out Trait3_gctb_run2_nopcs > Trait3_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T4
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T4.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T4.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  4 --bayes S --S 0.041742 --pi 0.083743 --hsq 0.946288 --chain-length 41000 --burn-in 1000 --out Trait4_gctb_run2_nopcs > Trait4_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T5
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T5.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T5.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --mpheno  5 --bayes S --S -0.006329 --pi 0.099993 --hsq 0.843492 --chain-length 41000 --burn-in 1000 --out Trait5_gctb_run2_nopcs > Trait5_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T6
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T6.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T6.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  6 --bayes S --S -0.020324 --pi 0.097347 --hsq 0.907544 --chain-length 41000 --burn-in 1000 --out Trait6_gctb_run2_nopcs > Trait6_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T7
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T7.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T7.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  7 --bayes S --S 0.019377 --pi 0.098711 --hsq 0.678497 --chain-length 41000 --burn-in 1000 --out Trait7_gctb_run2_nopcs > Trait7_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T8
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T8.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T8.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  8 --bayes S --S 0.000469 --pi 0.099648 --hsq 0.655492 --chain-length 41000 --burn-in 1000 --out Trait8_gctb_run2_nopcs > Trait8_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T9
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T9.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T9.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  9 --bayes S --S -0.027205 --pi 0.098205 --hsq 0.784116 --chain-length 41000 --burn-in 1000 --out Trait9_gctb_run2_nopcs > Trait9_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T10
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T10.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T10.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  10 --bayes S --S -0.0003 --pi 0.098981 --hsq 0.816524 --chain-length 41000 --burn-in 1000 --out Trait10_gctb_run2_nopcs > Trait10_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T11
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T11.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T11.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  11 --bayes S --S 0.02486 --pi 0.095036 --hsq 0.644007 --chain-length 41000 --burn-in 1000 --out Trait11_gctb_run2_nopcs > Trait11_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T12
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T12.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T12.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  12 --bayes S --S -0.014082 --pi 0.09552 --hsq 0.940899 --chain-length 41000 --burn-in 1000 --out Trait12_gctb_run2_nopcs > Trait12_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T13
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T13.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T13.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  13 --bayes S --S 0.020671 --pi 0.092464 --hsq 0.94262 --chain-length 41000 --burn-in 1000 --out Trait13_gctb_run2_nopcs > Trait13_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T14
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T14.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T14.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  14 --bayes S --S 0.004644 --pi 0.102152 --hsq 0.664502 --chain-length 41000 --burn-in 1000 --out Trait14_gctb_run2_nopcs > Trait14_gctb_run2_nopcs.log 2>&1
	
								
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T15
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T15.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T15.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  15 --bayes S --S -0.02015 --pi 0.101991 --hsq 0.923564 --chain-length 41000 --burn-in 1000 --out Trait15_gctb_run2_nopcs > Trait15_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T16
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T16.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T16.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  16 --bayes S --S -0.008756 --pi 0.09121 --hsq 0.892266 --chain-length 41000 --burn-in 1000 --out Trait16_gctb_run2_nopcs > Trait16_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T17
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T17.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T17.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  17 --bayes S --S -0.001531 --pi 0.104461 --hsq 0.813063 --chain-length 41000 --burn-in 1000 --out Trait17_gctb_run2_nopcs > Trait17_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T18
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T18.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T18.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  18 --bayes S --S 0 --pi 0.099421 --hsq 0.83379 --chain-length 41000 --burn-in 1000 --out Trait18_gctb_run2_nopcs > Trait18_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T19
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T19.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T19.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  19 --bayes S --S -0.009899 --pi 0.096325 --hsq 0.782222 --chain-length 41000 --burn-in 1000 --out Trait19_gctb_run2_nopcs > Trait19_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T20
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T20.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T20.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  20 --bayes S --S -0.075748 --pi 0.097334 --hsq 0.720382 --chain-length 41000 --burn-in 1000 --out Trait20_gctb_run2_nopcs > Trait20_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T21
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T21.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T21.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  21 --bayes S --S -0.023204 --pi 0.102451 --hsq 0.71779 --chain-length 41000 --burn-in 1000 --out Trait21_gctb_run2_nopcs > Trait21_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T22
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T22.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T22.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  22 --bayes S --S 0.010999 --pi 0.095811 --hsq 0.534739 --chain-length 41000 --burn-in 1000 --out Trait22_gctb_run2_nopcs > Trait22_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T23
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T23.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T23.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  23 --bayes S --S 0.015226 --pi 0.10238 --hsq 0.838335 --chain-length 41000 --burn-in 1000 --out Trait23_gctb_run2_nopcs > Trait23_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T24
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T24.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T24.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  24 --bayes S --S -0.004547 --pi 0.106337 --hsq 0.609723 --chain-length 41000 --burn-in 1000 --out Trait24_gctb_run2_nopcs > Trait24_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T25
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T25.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T25.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --mpheno  25 --bayes S --S -0.011161 --pi 0.104307 --hsq 0.89715 --chain-length 41000 --burn-in 1000 --out Trait25_gctb_run2_nopcs > Trait25_gctb_run2_nopcs.log 2>&1
										
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T26
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T26.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T26.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  26 --bayes S --S 0.054643 --pi 0.097264 --hsq 0.676436 --chain-length 41000 --burn-in 1000 --out Trait26_gctb_run2_nopcs > Trait26_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T27
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T27.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T27.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  27 --bayes S --S -0.022996 --pi 0.10011 --hsq 0.91081 --chain-length 41000 --burn-in 1000 --out Trait27_gctb_run2_nopcs > Trait27_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T28
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T28.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T28.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  28 --bayes S --S 0.025281 --pi 0.101139 --hsq 0.713657 --chain-length 41000 --burn-in 1000 --out Trait28_gctb_run2_nopcs > Trait28_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T29
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T29.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T29.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  29 --bayes S --S 0.00648 --pi 0.098757 --hsq 0.699096 --chain-length 41000 --burn-in 1000 --out Trait29_gctb_run2_nopcs > Trait29_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T30
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T30.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T30.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  30 --bayes S --S 0.050493 --pi 0.098472 --hsq 0.532224 --chain-length 41000 --burn-in 1000 --out Trait30_gctb_run2_nopcs > Trait30_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T31
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T31.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T31.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  31 --bayes S --S -0.036476 --pi 0.100589 --hsq 0.792517 --chain-length 41000 --burn-in 1000 --out Trait31_gctb_run2_nopcs > Trait31_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T32
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T32.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T32.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  32 --bayes S --S 0.010143 --pi 0.102336 --hsq 0.877305 --chain-length 41000 --burn-in 1000 --out Trait32_gctb_run2_nopcs > Trait32_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T33
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T33.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T33.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --mpheno  33 --bayes S --S 0.00723 --pi 0.099523 --hsq 0.896003 --chain-length 41000 --burn-in 1000 --out Trait33_gctb_run2_nopcs > Trait33_gctb_run2_nopcs.log 2>&1
	
										
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T34
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T34.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T34.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  34 --bayes S --S 0.01449 --pi 0.09751 --hsq 0.655058 --chain-length 41000 --burn-in 1000 --out Trait34_gctb_run2_nopcs > Trait34_gctb_run2_nopcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T35
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T35.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T35.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  35 --bayes S --S -0.042688 --pi 0.108285 --hsq 0.618441 --chain-length 41000 --burn-in 1000 --out Trait35_gctb_run2_nopcs > Trait35_gctb_run2_nopcs.log 2>&1
	
										
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T36
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T36.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T36.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  36 --bayes S --S 0.023077 --pi 0.0955 --hsq 0.844099 --chain-length 41000 --burn-in 1000 --out Trait36_gctb_run2_nopcs > Trait36_gctb_run2_nopcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_nopcs_T37
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T37.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_nopcs_T37.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --mpheno  37 --bayes S --S 0.006594 --pi 0.091439 --hsq 0.776184 --chain-length 41000 --burn-in 1000 --out Trait37_gctb_run2_nopcs > Trait37_gctb_run2_nopcs.log 2>&1
	
									
##################
#10 PCs-run2
###############

#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T1
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T1.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T1.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  1 --bayes S --S -0.002955 --pi 0.096222 --hsq 0.836706 --chain-length 41000 --burn-in 1000 --out Trait1_gctb_run2_10pcs > Trait1_gctb_run2_10pcs.log 2>&1
								
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T2
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T2.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T2.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  2 --bayes S --S 0.010163 --pi 0.105106 --hsq 0.74367 --chain-length 41000 --burn-in 1000 --out Trait2_gctb_run2_10pcs > Trait2_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T3
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T3.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T3.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  3 --bayes S --S -0.010588 --pi 0.088209 --hsq 0.894152 --chain-length 41000 --burn-in 1000 --out Trait3_gctb_run2_10pcs > Trait3_gctb_run2_10pcs.log 2>&1
								
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T4
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T4.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T4.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  4 --bayes S --S -0.092388 --pi 0.08708 --hsq 0.889995 --chain-length 41000 --burn-in 1000 --out Trait4_gctb_run2_10pcs > Trait4_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T5
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T5.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T5.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  5 --bayes S --S 0.004912 --pi 0.100015 --hsq 0.826717 --chain-length 41000 --burn-in 1000 --out Trait5_gctb_run2_10pcs > Trait5_gctb_run2_10pcs.log 2>&1
										
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T6
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T6.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T6.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  6 --bayes S --S -0.023756 --pi 0.09813 --hsq 0.862617 --chain-length 41000 --burn-in 1000 --out Trait6_gctb_run2_10pcs > Trait6_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T7
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T7.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T7.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  7 --bayes S --S 0.01748 --pi 0.097444 --hsq 0.733258 --chain-length 41000 --burn-in 1000 --out Trait7_gctb_run2_10pcs > Trait7_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T8
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T8.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T8.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  8 --bayes S --S 0.013717 --pi 0.095591 --hsq 0.662112 --chain-length 41000 --burn-in 1000 --out Trait8_gctb_run2_10pcs > Trait8_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T9
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T9.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T9.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  9 --bayes S --S 0.085918 --pi 0.099447 --hsq 0.787219 --chain-length 41000 --burn-in 1000 --out Trait9_gctb_run2_10pcs > Trait9_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T10
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T10.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T10.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  10 --bayes S --S 0.032357 --pi 0.10169 --hsq 0.807969 --chain-length 41000 --burn-in 1000 --out Trait10_gctb_run2_10pcs > Trait10_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T11
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T11.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T11.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  11 --bayes S --S 0.012815 --pi 0.104439 --hsq 0.665287 --chain-length 41000 --burn-in 1000 --out Trait11_gctb_run2_10pcs > Trait11_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T12
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T12.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T12.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  12 --bayes S --S -0.062359 --pi 0.089378 --hsq 0.899961 --chain-length 41000 --burn-in 1000 --out Trait12_gctb_run2_10pcs > Trait12_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T13
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T13.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T13.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  13 --bayes S --S -0.057117 --pi 0.086677 --hsq 0.892799 --chain-length 41000 --burn-in 1000 --out Trait13_gctb_run2_10pcs > Trait13_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T14
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T14.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T14.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  14 --bayes S --S 0.054396 --pi 0.10144 --hsq 0.652466 --chain-length 41000 --burn-in 1000 --out Trait14_gctb_run2_10pcs > Trait14_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T15
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T15.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T15.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  15 --bayes S --S -0.025994 --pi 0.090884 --hsq 0.87202 --chain-length 41000 --burn-in 1000 --out Trait15_gctb_run2_10pcs > Trait15_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T16
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T16.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T16.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  16 --bayes S --S 0.014156 --pi 0.099758 --hsq 0.870953 --chain-length 41000 --burn-in 1000 --out Trait16_gctb_run2_10pcs > Trait16_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T17
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T17.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T17.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  17 --bayes S --S -0.020422 --pi 0.099232 --hsq 0.827222 --chain-length 41000 --burn-in 1000 --out Trait17_gctb_run2_10pcs > Trait17_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T18
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T18.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T18.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  18 --bayes S --S 0 --pi 0.10076 --hsq 0.825407 --chain-length 41000 --burn-in 1000 --out Trait18_gctb_run2_10pcs > Trait18_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T19
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T19.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T19.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  19 --bayes S --S 0.036811 --pi 0.098998 --hsq 0.757185 --chain-length 41000 --burn-in 1000 --out Trait19_gctb_run2_10pcs > Trait19_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T20
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T20.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T20.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  20 --bayes S --S 0.010713 --pi 0.098589 --hsq 0.730289 --chain-length 41000 --burn-in 1000 --out Trait20_gctb_run2_10pcs > Trait20_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T21
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T21.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T21.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  21 --bayes S --S -0.031622 --pi 0.095787 --hsq 0.666977 --chain-length 41000 --burn-in 1000 --out Trait21_gctb_run2_10pcs > Trait21_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T22
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T22.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T22.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  22 --bayes S --S -0.026981 --pi 0.096824 --hsq 0.52426 --chain-length 41000 --burn-in 1000 --out Trait22_gctb_run2_10pcs > Trait22_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T23
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T23.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T23.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  23 --bayes S --S 0.001339 --pi 0.101549 --hsq 0.838047 --chain-length 41000 --burn-in 1000 --out Trait23_gctb_run2_10pcs > Trait23_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T24
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T24.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T24.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  24 --bayes S --S 0.039561 --pi 0.100917 --hsq 0.589413 --chain-length 41000 --burn-in 1000 --out Trait24_gctb_run2_10pcs > Trait24_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T25
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T25.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T25.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  25 --bayes S --S -0.001749 --pi 0.101428 --hsq 0.862184 --chain-length 41000 --burn-in 1000 --out Trait25_gctb_run2_10pcs > Trait25_gctb_run2_10pcs.log 2>&1

#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T26
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T26.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T26.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno  pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  26 --bayes S --S 0.03 --pi 0.09 --hsq 0.634 --chain-length 41000 --burn-in 1000 --out Trait26_gctb_run2_10pcs > Trait26_gctb_run2_10pcs.log 2>&1
																				
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T27
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T27.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T27.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  27 --bayes S --S 0.000709 --pi 0.090646 --hsq 0.862711 --chain-length 41000 --burn-in 1000 --out Trait27_gctb_run2_10pcs > Trait27_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T28
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T28.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T28.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  28 --bayes S --S -0.012369 --pi 0.104833 --hsq 0.810847 --chain-length 41000 --burn-in 1000 --out Trait28_gctb_run2_10pcs > Trait28_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T29
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T29.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T29.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  29 --bayes S --S -0.014112 --pi 0.094288 --hsq 0.679365 --chain-length 41000 --burn-in 1000 --out Trait29_gctb_run2_10pcs > Trait29_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T30
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T30.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T30.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  30 --bayes S --S -0.007922 --pi 0.09758 --hsq 0.548834 --chain-length 41000 --burn-in 1000 --out Trait30_gctb_run2_10pcs > Trait30_gctb_run2_10pcs.log 2>&1
	
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T31
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T31.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T31.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  31 --bayes S --S 0.016343 --pi 0.104513 --hsq 0.802274 --chain-length 41000 --burn-in 1000 --out Trait31_gctb_run2_10pcs > Trait31_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T32
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T32.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T32.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  32 --bayes S --S -0.044981 --pi 0.111779 --hsq 0.853126 --chain-length 41000 --burn-in 1000 --out Trait32_gctb_run2_10pcs > Trait32_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T33
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T33.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T33.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  33 --bayes S --S -0.009024 --pi 0.094136 --hsq 0.835917 --chain-length 41000 --burn-in 1000 --out Trait33_gctb_run2_10pcs > Trait33_gctb_run2_10pcs.log 2>&1

									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T34
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T34.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T34.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  34 --bayes S --S -0.050112 --pi 0.107038 --hsq 0.650478 --chain-length 41000 --burn-in 1000 --out Trait34_gctb_run2_10pcs > Trait34_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T35
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T35.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T35.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  35 --bayes S --S -0.016886 --pi 0.098758 --hsq 0.614906 --chain-length 41000 --burn-in 1000 --out Trait35_gctb_run2_10pcs > Trait35_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T36
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T36.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T36.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  36 --bayes S --S 0.012684 --pi 0.100857 --hsq 0.833898 --chain-length 41000 --burn-in 1000 --out Trait36_gctb_run2_10pcs > Trait36_gctb_run2_10pcs.log 2>&1
									
#!/bin/sh
#SBATCH --job-name=gctb_n10pcs_T37
#SBATCH --ntasks=1
#SBATCH --time=100:00:00
#SBATCH --mem-per-cpu=20G
#SBATCH --error=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T37.err
#SBATCH --output=/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/slurm-log/apgv4/gctb_run2_10pcs_T37.out
cd /work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
module load compiler/gcc/4.9 openmpi/1.10 gctb/1.0
gctb --bfile pruned_r2_01_allchr_agpv4_n282_snpid_maf001_geno1 --pheno pheno_282_n37_new.txt --covar pca_maf001_geno1_pruned_r2_01_10pcs.txt --mpheno  37 --bayes S --S 0.014134 --pi 0.104447 --hsq 0.778507 --chain-length 41000 --burn-in 1000 --out Trait37_gctb_run2_10pcs > Trait37_gctb_run2_10pcs.log 2>&1
									





```

