---
title: "Pheno37-posteriors-analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

```{r}

####
#Visualize posteriors
####

myData=read.csv("~/Ziegler_mineral_GWAS/data/apgv4/Posteriors_37pheno.csv",header=T)
head(myData)
library(reshape2)
myData[max(myData$Pi_mean),]

library(ggplot2)

str(myData)

dodge <- position_dodge(width = 0.9)
limits_S <- aes(ymax = myData$S_mean + myData$S_sd,
              ymin = myData$S_mean - myData$S_sd)

attach(myData)

p1 <- ggplot(data = myData, aes(x = myData$Trait, y = myData$S_mean, fill=PCs, group = PCs))
p1

##S
p1=p1+ geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(limits_S, position = dodge, width = 0.25) + ylim (-1.0,1.0) +
  xlab ("Traits") +
  ylab ("S") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                                 size=10, angle=45, vjust=0.95, hjust=0.95))
p1

pdf("Posterior_S_37pheno.pdf", height=6, width=12)
p1
dev.off()


##Pi

limits_Pi <- aes(ymax = myData$Pi_mean + myData$Pi_sd,
                ymin = myData$Pi_mean - myData$Pi_sd)

p2 <- ggplot(data = myData, aes(x = myData$Trait, y = myData$Pi_mean, fill=PCs, group = PCs))

p2=p2+ geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(limits_Pi, position = dodge, width = 0.25) + ylim (0,0.5) +
  xlab ("Traits") +
  ylab ("Pi") +
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                                   size=10, angle=45,vjust=0.95, hjust=0.95))
p2

pdf("Posterior_Pi_37pheno.pdf", height=6, width=12)
p2
dev.off()

##hsq

limits_hsq <- aes(ymax = myData$hsq_mean + myData$hsq_sd,
                 ymin = myData$hsq_mean - myData$hsq_sd)

p3 <- ggplot(data = myData, aes(x = myData$Trait, y = myData$hsq_mean, fill=PCs, group = PCs))

p3=p3+ geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(limits_hsq, position = dodge, width = 0.25) + ylim (0,1) +
  xlab ("Traits") +
  ylab ("hsq") +
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                                   size=10, angle=45,vjust=0.95, hjust=0.95))
p3

pdf("Posterior_hsq_37pheno.pdf", height=6, width=12)
p3
dev.off()

'''#####
#mcmc runs
#####


library(cowplot)
library(ggplot2)
library("tidyr")
cbPalette=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

get_gctb_log <- function(path="~/Ziegler_mineral_GWAS/data/apgv4/Traits_log"){

  files <- list.files(path, pattern="log", full.names = TRUE)
  message(sprintf("###>>> [%s] files detected!", length(files)))
  
res <- data.frame()
for(i in 1:length(files)){
  ### read in the file by skip the first two rows:
  pres <- read.table(files[i],header=F,fill=T,skip=38)
  pres$file <- files[i]
  pres$trait <- gsub(".*/|.log", "", pres$file)
  res <- rbind(res, pres)
}
return(res)
}


out <- get_gctb_log(path="~/Ziegler_mineral_GWAS/data/apgv4/Traits_log")
library(data.table)

fwrite(out,"gctb_bayesS_37phenologs.csv",sep=",")

df1=read.csv("gctb_bayesS_37phenologs.csv",header=T)

head(df1)

df1=subset(df1,select=c(14,1:13))'''





##########################################
#Compare bayesC with bayesS for 3 traits
##########################################

rm(list=ls())
cp1=read.csv("~/Ziegler_mineral_GWAS/data/apgv4/Post_bayescVsS.csv")


dodge <- position_dodge(width = 0.9)

attach(cp1)
str(cp1)
head(cp1)
##Pi
library(ggplot2)

limits_Pi <- aes(ymax = cp1$Pi_mean + cp1$Pi_sd,
                 ymin = cp1$Pi_mean - cp1$Pi_sd)

p2 <- ggplot(data = cp1, aes(x = cp1$Trait, y = cp1$Pi_mean,fill=PCs, group=PCs))

p2=p2+ geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(limits_Pi, position = dodge, width = 0.25) + 
  xlab ("Traits") +
  ylab ("Pi") +
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                                   size=10, angle=45,vjust=0.95, hjust=0.95))
p2

str(cp1)



pdf("Posterior_Pi_37pheno.pdf", height=6, width=12)
p2
dev.off()

##hsq

limits_hsq <- aes(ymax = cp1$hsq_mean + cp1$hsq_sd,
                  ymin = cp1$hsq_mean - cp1$hsq_sd)

p3 <- ggplot(data = cp1, aes(x = cp1$Trait, y = cp1$hsq_mean, fill=PCs, group = PCs))

p3=p3+ geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(limits_hsq, position = dodge, width = 0.25)+
  xlab ("Traits") +
  ylab ("hsq") +
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                                   size=10, angle=45,vjust=0.95, hjust=0.95))
p3

pdf("Posterior_hsq_37pheno.pdf", height=6, width=12)
p3
dev.off()

library(gridExtra)

grid.arrange(p2, p3, nrow = 1)

pdf("bayesSvsC.pdf")
grid.arrange(p2, p3, ncol = 1)
dev.off()

##########################################
#Get the correlations for 37 traits
##########################################       
#install.packages("corrplot")
library(corrplot)
#zie_282=zie_282[,-c(1:5)]

df1=read.table("~/Ziegler_mineral_GWAS/data/apgv4/pheno_282_n37_new.txt",header=T)
head(df1)
df1=as.data.frame(df1)

df2 <- cor(df1[,c(3:ncol(df1))],use = "na.or.complete")

??corrplot
corr_coef=round(df2,digits=2)
corr_coef
write.csv(corr_coef,file="/Users/rkastooriramamurth2/Ziegler_mineral_GWAS/graphs/Correlation_coefficients_Ziegler_complete.csv")


'''require(ggpubr)
require(tidyverse)
install.packages("Hmisc")
require(Hmisc)

cor_5 <- rcorr(as.matrix(df1[,c(3:ncol(df1))]))
M <- cor_5$r
p_mat <- cor_5$P
corrplot(M, method = "color", type = "upper", order = "hclust", 
         p.mat = p, sig.level = 0.01)

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(df2, method = "color", col = col(200),  
         type = "upper", order = "hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "darkblue", tl.srt = 45, #Text label color and rotation
         # Combine with significance level
         p.mat = p, sig.level = 0.01,  
         # hide correlation coefficient on the principal diagonal
         diag = FALSE 
)'''


rm(list=ls())

pdf("testcorr.pdf",height=14, width = 18)
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(df2, method = "color", col = col(200),  
         type = "upper", order = "hclust", 
         addCoef.col = "black", 
         number.cex = 0.8,
         number.font = 2,
         cl.cex = 1.5, # Add coefficient of correlation
         tl.col = "darkblue", tl.srt = 30, tl.cex=1, #Text label color and rotation
         # Combine with significance level
         #p.mat = cor_2$P , sig.level = 0.01,  
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)

dev.off()

##################################
##subset the SNP effects by mafs
##################################

cd /lustre/work/jyanglab/raghu/jyang/projects/Ziegler_mineral_GWAS/largedata/apgv4/
  
#Work on 8 traits prot, x20wt, no. of tillers per plant, plant height, upper leaf angle, ear length, ear weight and KRN
  
library(data.table)
df2=fread("Trait20_gctb_run2_nopcs.snpRes",header=F)

#colnames(df2) <-c("X","Name","Chrom","Position","Freq","Effect","SE")


#####
#NOTP-nopcs
#####

library(data.table)
df2=fread("Trait22_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4



########
#NOTP-withpcs
########

rm(list=ls())

library(data.table)
df2=fread("Trait22_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4


#######
#prot-nopcs
#######

rm(list=ls())

library(data.table)
df2=fread("Trait20_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4

######
#prot-10pcs
######

rm(list=ls())

library(data.table)
df2=fread("Trait20_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4


#######
#x20-wt-nopcs
#######
rm(list=ls())

library(data.table)
df2=fread("Trait37_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4


#######
#x20-wt-10pcs
#######
rm(list=ls())
library(data.table)
df2=fread("Trait37_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4 <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4


##########################################################


#####
#Earlength-nopcs
#####
rm(list=ls())
library(data.table)
df2=fread("Trait7_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_earlength_nopcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_earlength_nopcs



########
#Earlength-withpcs
########

rm(list=ls())

library(data.table)
df2=fread("Trait7_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_earlength_withpcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_earlength_withpcs


#######
#Upperleafangle-nopcs
#######

rm(list=ls())

library(data.table)
df2=fread("Trait36_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_ULA_nopcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_ULA_nopcs

######
#Upperleafangle-10pcs
######

rm(list=ls())

library(data.table)
df2=fread("Trait36_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_ULA_withpcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_ULA_withpcs


#######
#KRN_nopcs
#######
rm(list=ls())
library(data.table)
df2=fread("Trait8_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_KRN_nopcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_KRN_nopcs


#######
#KRN-10pcs
#######
rm(list=ls())
library(data.table)
df2=fread("Trait8_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_KRN_withpcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_KRN_withpcs 

#######################################################################


#######
#Earweight-nopcs
#######

rm(list=ls())

library(data.table)
df2=fread("Trait9_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_Earweight_nopcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_Earweight_nopcs

######
#Earweight-10pcs
######

rm(list=ls())

library(data.table)
df2=fread("Trait9_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_Earweight_10pcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_Earweight_10pcs


#######
#Pltht_nopcs
#######
rm(list=ls())

library(data.table)
df2=fread("Trait23_gctb_run2_nopcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_Pltht_nopcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_Pltht_nopcs


#######
#Pltht-10pcs
#######
rm(list=ls())
library(data.table)
df2=fread("Trait23_gctb_run2_10pcs.snpRes")
length(df2$Name)
df4=df2[which(Freq<=0.1),]
length(df4$Name)
df4 <-  transform(df4, group=cut(Freq, breaks=c(-Inf, 0.01, 0.02, 0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1,Inf),
labels=c("<0.01",0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)))
head(df4)
res3 <-do.call(data.frame,aggregate(df4$Effect~group, df4, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res3
df5=df2[which(Freq<= 1),]
df5 <-  transform(df5, group=cut(Freq, breaks=c(-Inf, 0.1, 0.2, 0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,Inf),
labels=c("<0.1",0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)))
head(df5)
res4_Pltht_10pcs <-do.call(data.frame,aggregate(df5$Effect~group, df5, 
FUN=function(x) c(Count=length(x), Sum=sum(x))))
res4_Pltht_10pcs



rm(list=ls())
df=read.csv("~/Ziegler_mineral_GWAS/data/apgv4/mafandeffectsize.csv")
head(df)

attach(df)
str(df)

df=as.data.frame(df)
df[,4]=as.numeric(df[,4])

install.packages("Scale")
library(Scale)

df[,4]=scale(df[,4])

?scale

?apply
head(df[,4])
library(ggplot2)
# Basic histogram

pdf("MAFandEffects_37pheno.pdf",height=15, width=20)
ggplot(df, aes(x=Freq,y=Effect)) + geom_bar(stat = "identity") + facet_wrap(~Trait)
  dev.off()


```

